\documentclass{beamer}
\usepackage[utf8]{inputenc}
%\usepackage{ru} 
%RU package can be found at website of the RU.  Just use Google: 'RU LateX Beamer template.'

\usepackage{graphicx}

\title{Traffic Simulation using Cellular Automata}
\institute[Radboud University Nijmegen]{Radboud University Nijmegen}
\author{Hue Dang \\ Athena Iakovide \\ Olivier Schnitzeler}



\begin{document}
\begin{frame}
	\titlepage
\end{frame}

\begin{frame}
	\frametitle{Overview}
	\tableofcontents
\end{frame}

\section{Problem}
\begin{frame}
\frametitle{Problem}
\bf{Goal:} Model two-lane high way traffic stuation using cellular automata.\\
\bf{Properties of the model:}'\\
\begin{itemize}
	\item Cars must be able to adapt speed depending on traffic density.
	\item Cars must be able to switch lanes. 
	\item Cars must be able to merge in case one of two lanes if blocked.
	\item Cars must be able to come to a full stop in case of a road block.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Research on the topic}
% LITERATURE WE USED
% The research so far, using CA, doesn't handle forced lane changing. That is our main goal.
\bf{Existing research on traffic simulation with CA:}
\begin{itemize}
	\item Rules for one-lane traffic situation.
	\item Rules for merging behaviour. 
	\item ?
\end{itemize}
\\
Our problem extends current research, because we will have forced mergin (road blocks, on-coming ramps).
\end{frame}



\section{Approach}
\begin{frame}
% REPRESENTATION OF THE PROBLEM
\frametitle{Representation of the problem}
\large{Micro versus Macro}
\begin{itemize}
\item Road represented by cells.
\item A car is an occupied cell. 
\item Possible state cells:
\begin{itemize}
	\item Free
	\item Occupied - the state of the cell is represented by the speed of the car. 
\end{itemize}
\end{itemize}
\end{frame}


\section{First results}
\begin{frame}
\frametitle{First results}
%MAKE SET OF SLIDES SHOWING SIMULATION.
\end{frame}



\section{Issues}
\begin{frame}
\frametitle{Issues so far}
\bf{Difficulties so far}
\begin{itemize}
\item Defining the safety-gap between car.
\item The cells don't have memory; speed estimation is difficult. 
\end{itemize}
\end{frame}


\section{What's next?}
\begin{frame}
\frametitle{Aspects to implement next}
\bf{Future implementations}
\begin{itemize}
\item Simulate forced lane changing, by means of an oncoming ramp / road block.
\item Apply a set of traffic rules (American / German)
\item Implement sleepy driver - one that uses distance to car in front, instead of speed of car in front
\end{itemize}
\end{frame}

\section{Discussion}
\begin{frame}
\frametitle{Questions?}
\begin{center}
Any questions?
\end{center}
\end{frame}

\end{document}
